Flexible Scientific Data Management for Plant Phenomics Research

### 2013-04-15 s4biodiv2013/Rebuttals.txt

 *****

 I would have been far more supportive of the manuscript if it had described some of their models; explained how the models take advantage of other ontologies (and which); explained which aspects of the data they semantically annotate, why, and how successfully; and how this relates to biodiversity.

 *****

 Rebuttal: There are no measures to define the successful use of external ontologies, as the definitions of external ontologies are always in part defined by the community based on both discussions and based on the way they are used. The set of ontologies that are currently in use is described in Figure 2.

@@

The manuscript also feels like it was written by someone extremely familiar with the system, as it uses phraseology that likely only has meaning to them.  For example "External ontologies must currently be mapped into the PODD system to define the expected status of the classes and properties with respect to the basic PODD concepts" - I have read that sentence multiple times and still cannot decypher what it means to "define the expected status of the classes and properties", or what the authors mean by "mapping" external ontologies "into" the PODD system.  Other examples of this include:

"allow scientists to generate datasets before they were certain about the semantic meaning of their work" - what does that mean?

 *****

 Rebuttal : Rewrote Section 5 Paragraph 2 to include an example of mapping the Crop Ontology into PODD.

### 2013-04-15 s4biodiv2013/PODD-S4BIODIV-Submission.tex
rewrite Section 5 p2 to include Crop Ontology example

External ontologies must currently be mapped into the PODD system to define the
expected status of the classes and properties with respect to the basic PODD
concepts. The basic concepts are used to both verify that each PODD project has
a single valid tree structure, and render HTML pages for both browsing and
editing. PODD also supports an RDF-based HTTP REST interface that clients may
use to fetch and update objects.
% without using the HTML pages.

>>>>

Subsets of phenomics ontologies such as the Plant Ontology and the Crop Ontology 
were mapped into PODD by adding OWL constraints. These constraints enable PODD to
verify that the use of classes and properties from these ontologies was consistent 
with the PODD ontology. For example, the Crop Ontology contains a class defining 
soil as ``Sandy Loam'', giving it the identifier ``0000104''. This was mapped into 
PODD to define a particular soil sample as being Sandy Loam using the triple:
$poddSampleSandyLoamSoil\ a\ cropOntology:\_0000104 .$

%External ontologies must currently be mapped into the PODD system to define the
%expected status of the classes and properties with respect to the basic PODD
%concepts. The basic concepts are used to both verify that each PODD project has
%a single valid tree structure, and render HTML pages for both browsing and
%editing. PODD also supports an RDF-based HTTP REST interface that clients may
%use to fetch and update objects.
% without using the HTML pages.
